---
title: "project2"
author: "Zhenjie Zhao, Zhenpeng Liu"
date: "November 27, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Read the dataset from the file
```{r}
rawTokenData <- read.table("/Users/J/Desktop/6313.18f/project2/networktenxpayTX.txt", header = FALSE)
colnames(rawTokenData) <- c("fromNodeID", "toNodeID", "tunixTime", "ttokenAmount")
tokendataNoOutliers <- subset(rawTokenData, ttokenAmount <= 1.09347861e+26)
tokenData <- tokendataNoOutliers
rowNumber <- nrow(tokenData)
priceData <- read.table("/Users/J/Desktop/6313.18f/project2/tenxpay.txt", header = FALSE)
colnames(priceData) <- c("Date", "Open", "High", "Low", "Close", "Volume", "Market Cap")

totalTran <- nrow(tokendataNoOutliers)
maxt <- 1.09347861e+26
```

# Convert UNIX epoch to Date object and initializing the data for analysis
The data is initialized by taking the feature data one day in advance, which is convinient for the feature extraction.
```{r}
tokenData$tunixTime = as.POSIXct(tokenData$tunixTime,origin = "1970-01-01",tz = "GMT")
tokenData$tunixTime = format(tokenData$tunixTime, format="%Y-%m-%d")
tokenData$tunixTime = as.Date(tokenData$tunixTime, format="%Y-%m-%d")
tokenDataInDate <- tokenData
head(tokenDataInDate)
priceDataFormated <- priceData
priceDataFormated$Date = as.Date(priceDataFormated$Date, format="%m/%d/%Y")
priceDataFormated <- priceDataFormated[order(priceDataFormated$Date),]
priceDataFormated$open_return <- priceDataFormated$Open[-1] / priceDataFormated$Open - 1
priceDataFormated$close_return <- priceDataFormated$Close[-1] / priceDataFormated$Close - 1
priceDataFormated$open_return_prev <- priceDataFormated$open_return
priceDataFormated$close_return_prev <- priceDataFormated$close_return
priceDataFormated <- na.omit(transform(priceDataFormated, open_return_prev = c(0, open_return_prev[-nrow(priceDataFormated)])))
priceDataFormated <- na.omit(transform(priceDataFormated, close_return_prev = c(0, close_return_prev[-nrow(priceDataFormated)])))
head(priceDataFormated)
```


# Keep the data between 2017-06-27 and 2018-05-06 which is the overlapping of the token and price
```{r}
priceStartDate <- min(priceDataFormated$Date)
tokenStartDate <- min(tokenDataInDate$tunixTime)
priceEndDate <- max(priceDataFormated$Date)
tokenEndDate <- max(tokenDataInDate$tunixTime)
startDate <- max(priceStartDate, tokenStartDate)
endDate <- min(priceEndDate, tokenEndDate)
priceDataFormated <- subset(priceDataFormated, Date >= startDate & Date <= endDate)
tokenDataInDate <- subset(tokenDataInDate, tunixTime >= startDate & tunixTime <= endDate)
```

# Extract features
The following features are extracted as alternatives for the regression analysis.
open_return: open price's growth rate from t-2 day to t-1 day; 
close_return: price's growth rate from t-2 day to t-1 day; 
HML: the difference between the high price and the low price on t-1 day; 
CMO: the difference between the close price and the open price on t-1 day;
total_transfer_time: number of transactions on t-1 day; 
mt10_time: percentage of investors who bought more than 10 tokens on t-1 day;
Volume:trading volume on t-1 day.
```{r}
library(plyr)
tranferTimes <- count(tokenDataInDate, "tunixTime")
tokenDataInDate_mt10 <- subset(tokenDataInDate, ttokenAmount > 10)
tranferTimes_mt10 <- count(tokenDataInDate_mt10, "tunixTime")
final_data <- merge(x=tranferTimes, y=tranferTimes_mt10, by.x="tunixTime", by.y="tunixTime")
colnames(final_data) <- c("Date","total_transfer_time", "mt10_time")
final_data <- merge(x=final_data, y=priceDataFormated, by.x="Date", by.y="Date")
final_data$CMO <- final_data$Close - final_data$Open
final_data$HML <- final_data$High - final_data$Low
  
```

# Feature analysis
The following figure is the correlation between each pair in the order of ["open_return","open_return_prev","HML","CMO", "total_transfer_time", "mt10_time", "Volume"]
```{r}
library(psych)
pairs.panels(final_data[c("open_return","close_return","HML","CMO", "total_transfer_time", "mt10_time", "Volume")]) 
```

# Multiple regression analysis
After trying some combinations, we found open_return ~ mt10_time + HML + CMO is a good one which performs better than others.
```{r}
#ins_model <- lm(price_return~per_tranferTimes+per_ivst_mt10+per_HmL+price_return,data=features)
ins_model <- lm(open_return~mt10_time+HML+CMO,data=final_data)
ins_model 
summary(ins_model)
```

The Residuals section provides the main statistics of the prediction errors. In our model, the median residuals is -0.00197 which is small enough to prove the accuracy of the model;
The asterisk mark represents the predictive power of each feature in the model. Most of the features in the model has 2 or 3 asterisk marks, which provides a strong predictive power of each feature in the model;
The Multiple R-squared values (also known as decision coefficients) provide a way to measure the performance of a model, that is, how well the model can interpret the values of dependent variables as a whole. In our model, the Multiple R-squared value is 0.5218, the Adjusted R-squared value is 0.5172, which are high enough to present that performance of our model is good and satisfactory.

