---
title: "Project1Q2"
author: "Zhenjie Zhao, Zhenpeng Liu"
date: "October 24, 2018"
output: html_document
---

# Group Members
Zhenjie Zhao (zxz170530) , Zhenpeng Liu (zxl171630)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Primary Token Selection
The UTD-ID of the memebers are 2021373350 and 2021377521, so the sum of the ID numbers and mod 20 results in 11. Then the 11th largest file networktenxpayTX.txt is selected.

#Import data from the file and remove the outliers. 
We modified a little bit of the header of the price data file in order to import it successfully
```{r}
rawTokenData <- read.table("/Users/J/Desktop/6313.18f/project1/networktenxpayTX.txt", header = FALSE)
colnames(rawTokenData) <- c("fromNodeID", "toNodeID", "tunixTime", "ttokenAmount")
tokendataNoOutliers <- subset(rawTokenData, ttokenAmount <= 1.09347861e+26)
tokenData <- tokendataNoOutliers
rowNumber <- nrow(tokenData)
priceData <- read.table("/Users/J/Desktop/6313.18f/project1/tenxpay.txt", header = FALSE)
colnames(priceData) <- c("Date", "Open", "High", "Low", "Close", "Volume", "Market Cap")
totalTran <- nrow(tokendataNoOutliers)
maxt <- 1.09347861e+26
```

# Outliers
In the dataset tenxpayTX, there is one outlier.

```{r}
outliers <- subset(rawTokenData, ttokenAmount >= 1.09347861e+26)
head(outliers)
```

# Convert UNIX epoch to Date object
```{r}
tokenData$tunixTime = as.POSIXct(tokenData$tunixTime,origin = "1970-01-01",tz = "GMT")
tokenData$tunixTime = format(tokenData$tunixTime, format="%Y-%m-%d")
tokenData$tunixTime = as.Date(tokenData$tunixTime, format="%Y-%m-%d")
tokenDataInDate <- tokenData
head(tokenDataInDate)
priceDataFormated <- priceData
priceDataFormated$Date = as.Date(priceDataFormated$Date, format="%m/%d/%Y")
head(priceDataFormated)
```

# Keep the data between 2017-06-27 and 2018-05-06 which is the overlapping of the token and price
```{r}
priceStartDate <- min(priceDataFormated$Date)
tokenStartDate <- min(tokenDataInDate$tunixTime)
priceEndDate <- max(priceDataFormated$Date)
tokenEndDate <- max(tokenDataInDate$tunixTime)
startDate <- max(priceStartDate, tokenStartDate)
endDate <- min(priceEndDate, tokenEndDate)
```

# 1st try to creat layers - 100 layers
```{r}
layer0 <- tokenDataInDate
layer1 <- subset(tokenDataInDate, ttokenAmount <= 0.01 * maxt)
layer2 <- subset(tokenDataInDate, ttokenAmount > 0.01 * maxt & ttokenAmount <= 0.02 * maxt)
layer3 <- subset(tokenDataInDate, ttokenAmount > 0.02 * maxt & ttokenAmount <= 0.03 * maxt)
layer4 <- subset(tokenDataInDate, ttokenAmount > 0.03 * maxt & ttokenAmount <= 0.04 * maxt)
layer5 <- subset(tokenDataInDate, ttokenAmount > 0.04 * maxt & ttokenAmount <= 0.05 * maxt)
layer6 <- subset(tokenDataInDate, ttokenAmount > 0.05 * maxt & ttokenAmount <= 0.06 * maxt)
layer7 <- subset(tokenDataInDate, ttokenAmount > 0.06 * maxt & ttokenAmount <= 0.07 * maxt)
layerEmpty <- subset(tokenDataInDate, ttokenAmount > 0.07 * maxt)
```

# Data distribution for layers
```{r}
library(ggplot2)
ggplot(NULL,aes(x=tunixTime, y=ttokenAmount),color = layer) +
geom_point(data = layer1, color = "red") +
geom_point(data = layer2, color = "orange") +
geom_point(data = layer3, color = "yellow") +
geom_point(data = layer4, color = "green") +
geom_point(data = layer5, color = "blue") +
geom_point(data = layer6, color = "purple") +
geom_point(data = layer7, color = "grey") +
labs(title="Data distribution for layers", x="Time", y="Number of Transactions")
```


# Calculate tranfertimes of each layer
```{r}
library(plyr)
tranferTimes0 <- count(layer0, "tunixTime")
head(tranferTimes0)
tranferTimes0 <- subset(tranferTimes0, tunixTime >= startDate & tunixTime <= endDate)
priceDataFormated <- subset(priceDataFormated, Date >= startDate & Date <= endDate)

tranferTimes1 <- count(layer1, "tunixTime")
head(tranferTimes1)
tranferTimes1 <- subset(tranferTimes1, tunixTime >= startDate & tunixTime <= endDate)
priceDataFormated <- subset(priceDataFormated, Date >= startDate & Date <= endDate)

tranferTimes2 <- count(layer2, "tunixTime")
head(tranferTimes2)
tranferTimes2 <- subset(tranferTimes2, tunixTime >= startDate & tunixTime <= endDate)
priceDataFormated <- subset(priceDataFormated, Date >= startDate & Date <= endDate)

tranferTimes3 <- count(layer3, "tunixTime")
head(tranferTimes3)
tranferTimes3 <- subset(tranferTimes3, tunixTime >= startDate & tunixTime <= endDate)
priceDataFormated <- subset(priceDataFormated, Date >= startDate & Date <= endDate)

tranferTimes4 <- count(layer4, "tunixTime")
head(tranferTimes4)
tranferTimes4 <- subset(tranferTimes4, tunixTime >= startDate & tunixTime <= endDate)
priceDataFormated <- subset(priceDataFormated, Date >= startDate & Date <= endDate)

tranferTimes5 <- count(layer5, "tunixTime")
head(tranferTimes5)
tranferTimes5 <- subset(tranferTimes5, tunixTime >= startDate & tunixTime <= endDate)
priceDataFormated <- subset(priceDataFormated, Date >= startDate & Date <= endDate)

tranferTimes6 <- count(layer6, "tunixTime")
head(tranferTimes6)
tranferTimes6 <- subset(tranferTimes6, tunixTime >= startDate & tunixTime <= endDate)
priceDataFormated <- subset(priceDataFormated, Date >= startDate & Date <= endDate)

tranferTimes7 <- count(layer7, "tunixTime")
head(tranferTimes7)
tranferTimes7 <- subset(tranferTimes7, tunixTime >= startDate & tunixTime <= endDate)
priceDataFormated <- subset(priceDataFormated, Date >= startDate & Date <= endDate)

tranferTimesOthers <- count(layerEmpty, "tunixTime")
head(tranferTimesOthers)
tranferTimesOthers <- subset(tranferTimesOthers, tunixTime >= startDate & tunixTime <= endDate)
priceDataFormated <- subset(priceDataFormated, Date >= startDate & Date <= endDate)
```

# mergedData
```{r}
mergedData0 <- merge(x=tranferTimes0, y=priceDataFormated, by.x="tunixTime", by.y="Date")

mergedData1 <- merge(x=tranferTimes1, y=priceDataFormated, by.x="tunixTime", by.y="Date")

mergedData2 <- merge(x=tranferTimes2, y=priceDataFormated, by.x="tunixTime", by.y="Date")

mergedData3 <- merge(x=tranferTimes3, y=priceDataFormated, by.x="tunixTime", by.y="Date")

mergedData4 <- merge(x=tranferTimes4, y=priceDataFormated, by.x="tunixTime", by.y="Date")

mergedData5 <- merge(x=tranferTimes5, y=priceDataFormated, by.x="tunixTime", by.y="Date")

mergedData6 <- merge(x=tranferTimes6, y=priceDataFormated, by.x="tunixTime", by.y="Date")

mergedData7 <- merge(x=tranferTimes7, y=priceDataFormated, by.x="tunixTime", by.y="Date")

mergedDataOthers <- merge(x=tranferTimesOthers, y=priceDataFormated, by.x="tunixTime", by.y="Date")
```

#calculate the correlation
```{r}
cor(mergedData0$Open,mergedData0$freq)

cor(mergedData1$Open,mergedData1$freq)

cor(mergedData2$Open,mergedData2$freq)

cor(mergedData3$Open,mergedData3$freq)

cor(mergedData4$Open,mergedData4$freq)

cor(mergedData5$Open,mergedData5$freq)

cor(mergedData6$Open,mergedData6$freq)

cor(mergedData7$Open,mergedData7$freq)

cor(mergedDataOthers$Open,mergedDataOthers$freq)
```

# 2nd try to create layer
#Distribution of the transaction amount in logistic scale
Due to the high range of the data, we preprocess the data by log10()
```{r}
logtokens <- log10(tokendataNoOutliers$ttokenAmount)
hist(logtokens)
```


#Create layer and get the data between two layers
The data is divided by 10 layers with different order of magnitude.
We use loop to calculate different The result of each layer is stored in tempResult
```{r}
maxamount <- 7.108079e+24

layerLeft <- maxamount*c(1.0e-1, 1.0e-2, 1.0e-3, 1.0e-4, 1.0e-5, 1.0e-6, 1.0e-7, 1.0e-8, 1.0e-9, 1.0e-10)

layerRight <- maxamount*c(1.0e0, 1.0e0, 1.0e0, 1.0e0, 1.0e0, 1.0e0, 1.0e0, 1.0e0, 1.0e0, 1.0e0)
#layerRight <- maxamount*c(1.0e0, 1.0e-1, 1.0e-2, 1.0e-3, 1.0e-4, 1.0e-5, 1.0e-6, 1.0e-7, 1.0e-8, 1.0e-9)
tempResult <- data.frame(LeftBound = double(),
                         RightBound = double(),
                         numOfTransaction = integer(),
                         ratio = double(),
                         corOfOpen = double(),
                         corOfClose = double(),
                         corOfHigh = double(),
                         corOfLow = double(),
                         corOfHML = double(),
                         corOfOMC = double())

i <- 0
for(left in layerLeft){
  i <- i + 1
  right <- layerRight[i]
  tokenDataLeft <- subset(rawTokenData, ttokenAmount <= right)
  tokenDataFiltered <- subset(tokenDataLeft, ttokenAmount >= left)
  numOfTran <- nrow(tokenDataFiltered)
  ratio <- numOfTran/totalTran
  #change the format of Date
  tokenDataFiltered$tunixTime = as.POSIXct(tokenDataFiltered$tunixTime,origin = "1970-01-01",tz = "GMT")
  tokenDataFiltered$tunixTime = format(tokenDataFiltered$tunixTime, format="%Y-%m-%d")
  tokenDataFiltered$tunixTime = as.Date(tokenDataFiltered$tunixTime, format="%Y-%m-%d")
  
  library(plyr)
  tranferTimes <- count(tokenDataFiltered, "tunixTime")
  priceDataFormated <- priceData
  priceDataFormated$Date = as.Date(priceDataFormated$Date, format="%m/%d/%Y")
  
  #find the boundary of the date
  priceStartDate <- min(priceDataFormated$Date)
  tokenStartDate <- min(tranferTimes$tunixTime)
  priceEndDate <- max(priceDataFormated$Date)
  tokenEndDate <- max(tranferTimes$tunixTime)
  #merge the data by date
  tranferTimes <- subset(tranferTimes, tunixTime >= priceStartDate & tunixTime >= tokenStartDate & tunixTime <= priceEndDate & tunixTime <= tokenEndDate)
  priceDataFormated <- subset(priceDataFormated, Date >= priceStartDate & Date >= tokenStartDate & Date <= priceEndDate & Date <= tokenEndDate)
  mergedData <- merge(x=tranferTimes, y=priceDataFormated, by.x="tunixTime", by.y="Date")
  #calculate the correlation with different features
  openCor <- cor(mergedData$Open, mergedData$freq) #correlation between number of transactions and open price
  closeCor <- cor(mergedData$Close, mergedData$freq) #correlation between number of transactions and close price
  highCor <- cor(mergedData$High, mergedData$freq) #correlation between number of transactions and high price
  lowCor <- cor(mergedData$Low, mergedData$freq) #correlation between number of transactions and low price
  HMLCor <- cor(mergedData$High - mergedData$Low, mergedData$freq) #correlation between number of transactions and high price - low price
  OMCCor <- cor(mergedData$Open - mergedData$Close, mergedData$freq) #correlation between number of transactions and open price - close price
  
  
  #store the result
  tempResult[i,] <- c(left, right, numOfTran, ratio, openCor, closeCor,  highCor, lowCor, HMLCor, OMCCor)
  
}

```

#Result
```{r}
tempResult
```

#Conclusion
Referring to the result, we found that the number of transactions and high price - low price has high correlations when the amount of transaction increases. That means the more difference between high price and low price it is, the more transactions with huge amount will happen.

